Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-11-20 paper/paper.tex
Article Update
Article now includes diagram of current topology as provided by Emily.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

@@

The proposed design takes this simple concept and uses it to demonstrate a distributed system, whereby the two “players” are instead two teams of up to 5 players, which take turns to vote on where their team should place their markers. Each team has a designated "leader" which communicates data with their team's peers, and the opposing team's "leader" to synchronise current gameplay state. The leaders communicate the vote of their team to the opposing leader so that they may pass that result on to the peers of that team.

\section{Implementation}

>>>>

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.
\usepackage{graphicx}

@@

The proposed design takes this simple concept and uses it to demonstrate a distributed system, whereby the two “players” are instead two teams of up to 5 players, which take turns to vote on where their team should place their markers. Each team has a designated "leader" which communicates data with their team's peers, and the opposing team's "leader" to synchronise current gameplay state.

\begin{figure}[h]
	\includegraphics[width=\linewidth]{images/DAS-topology.png}
	\caption{Topology for Distributed Tic Tac Toe}
	\label{fig:topology1}
\end{figure}

The leaders communicate the vote of their team to the opposing leader so that they may pass that result on to the peers of that team, as pictured in figure 1.
\section{Implementation}
